\documentclass[english,11pt]{article}
\usepackage{babel}
\usepackage[utf8]{inputenc}
\usepackage{blindtext}
\usepackage{textcomp} 
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{geometry}
 \geometry{
 a4paper,
 right=19mm,
 bottom=19mm,
 left=32mm,
 top=19mm,
}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,titling,url,array}
\usepackage{physics}
\usepackage{color}
\usepackage{braket}
\usepackage{dsfont}
\usepackage{mathrsfs}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\theoremstyle{definition}
\newtheorem{defn}{Definición}[section]
\newtheorem{conj}{Conjecture}[section]
\newtheorem{exmp}{Example}[section]
\usepackage{float}
\usepackage{wrapfig}
\theoremstyle{plain}
\newtheorem{thm}{Teorema}[section]
\newtheorem{lem}[thm]{Lema}
\newtheorem{prop}[thm]{Proposition}
\newtheorem*{cor}{Corollary}

\begin{document}
\title{Story}
\maketitle
\begin{center}


\section*{progris riport l-martch 5 1965 }
\end{center}
Mr. Strauss says I shud rite down what I think and evrey thing that happins to me from now on. I dont know why but he says its importint so they will see if they will use me. I hope they use me. Miss Kinnian says maybe they can make me smart. I want to be smart. My name is Charlie Gordon. I am 37 years old and 2 weeks ago was my brithday. I have nuthing more to rite now so I will close for today.
\\ \\
\textit{In order to unlock the following chapter you should solve the following problem.} \\
\begin{center}
\textbf{The first problem will be released on April 29th of 2019.}
\end{center}
\end{document}